Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-24 manuscript.tex
Polish the paragraph on exoplanetary radio bursts.

\textbf{\emph{Searching for Exoplanetary Radio Bursts.}}
\label{sec:exoplanets}
HERA could be a powerful tool in the search for bright, highly polarized auroral bursts
from exoplanets %due to the electron cyclotron maser instability 
\citep{treumann2006,hallinan_et_al2015}. These
distinctive, coherent bursts occur periodically at the planetary
rotation rate, which cannot otherwise be measured. 
A burst from a terrestrial planet could point toward
habitability, since it implies a powerful magnetic field
protecting the atmosphere and perhaps the biosphere from energetic stellar wind
particles \citep{tarter_et_al2007}. HERA's sensitivity, large FoV, long campaigns, and precise calibration are all well-suited
for discovering exoplanetary radio bursts from Jupiter-like planets out to 25~pc. Many well studied exoplanetary systems within that distance are in the HERA stripe, including Fomalhaut, Gl 667 C, Gl 433, HD 147513, and Gl 317.

>>>>

\textbf{\emph{Searching for Exoplanetary Radio Bursts.}}
\label{sec:exoplanets}
HERA could revolutionize the study of extrasolar magnetospheres if it detects bright, highly polarized exoplanetary auroral radio bursts \citep{zarka2011}. Observers have tried to detect these distinctive events since even before the discovery of the first exoplanet \citep{winglee_et_al1986} but have thus far not succeeded. The bursts occur at the electron cyclotron frequency and are highly beamed, allowing remote sensing of planetary rotation periods and magnetic field strengths, two quantities that are otherwise only indirectly measurable. Since magnetic fields may play a key role in protecting atmospheres and/or biospheres from energetic stellar wind particles \citep[e.g.,][]{tarter_et_al2007}, studies of planetary magnetism may be vital to evaluating habitability. HERA's sensitivity, large field of view, long campaigns, and precise calibration make it well-suited to the search for radio bursts from Jupiter-like planets out to 25~pc. Well-studied exoplanet host stars in the HERA stripe within that distance include Fomalhaut, Gl~317, Gl~433, Gl~667~C, and HD~147513.
